\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}

\signature{Ali Subhan \\ Independent Researcher \\ Lahore, Pakistan \\ ORCID: 0009-0006-8800-5296 \\ \href{mailto:alisubhangenius@gmail.com}{alisubhangenius@gmail.com}}
\address{Ali Subhan \\ Lahore, Pakistan}

\begin{document}

\begin{letter}{To the Editors \\ Journal of Machine Learning Research (JMLR)}

\opening{Dear JMLR Editorial Board,}

I wish to submit my manuscript titled \textbf{``Compositional Transfer in Neural World Models via Symbolic Law Discovery''} for consideration as an original research article in the Journal of Machine Learning Research.

\textbf{Scientific Case:}\\
This paper addresses the foundational problem of zero-shot compositional transfer in physical world modeling. While existing monolithic methods like Physics-Informed Neural Operators (PINO) and Graph Neural Networks focus on high-fidelity interpolation within specific environments, they suffer from mathematical entanglement that precludes true algebraic composition. This work introduces the principle of \emph{Tangent-Space Residual Superposition}. By constraining neural dynamics models to learn physically isolated force-density residuals, this paper proves that deep networks can internalize independent physical laws (e.g., inverse-square gravity, linear spring limits, viscous drag) and seamlessly construct chaotic, unseen multi-physics environments zero-shot.

Furthermore, the manuscript demonstrates this utility by uncovering a rigorous \emph{Baseline Washout} scaling law ($\text{Gain} = 1.546 \cdot D^{-0.422}$). It provides analytical proof that monolithic architectures actively sacrifice target mechanisms for aggregate test-set expediency as phase-space dimensionality expands ($D=12$). By integrating SINDy (Sparse Identification of Nonlinear Dynamics) backends directly into our causal modules, the framework not only achieves a 1.63x predictive advantage over PINO but natively extracts the exact symbolic PDEs underlying the system ($99.25\%$ empirical accuracy), resolving the traditional trade-off between flexible neural world models and interpretable white-box science. I believe this work significantly advances the subfield of scientific machine learning by demonstrating that rigorous modular constraints are mathematically necessary for generalizing physics outside the training manifold.

\textbf{Required Disclosures:}
\begin{itemize}
    \item \textbf{Overlap:} This manuscript represents entirely novel, original research. It is not an extension of any prior conference publication, has not been published elsewhere, and is not currently under consideration by another journal.
    \item \textbf{Consent:} I, as the sole author, have reviewed and approved this submission to JMLR.
    \item \textbf{Conflicts:} I declare no financial or personal conflicts of interest. Specifically, I have not collaborated with any JMLR Action Editors in the past 5 years.
\end{itemize}

\textbf{Suggestions:}
\begin{itemize}
    \item \textbf{Suggested Action Editors:} Bernhard Schölkopf (Causal Representation Learning), Kun Zhang (Causal Discovery), or Finale Doshi-Velez (Interpretability/Symbolic Methods).
    \item \textbf{Suggested Reviewers:} Miles Cranmer (SINDy / Symbolic Physics), Peter Battaglia (Physics \& Graph Networks), taking care to avoid any direct institutional conflicts.
\end{itemize}

\textbf{Keywords:} Compositional Generalization, Causal Representation Learning, Scientific Machine Learning, Symbolic Law Discovery, Neural World Models.

Thank you for your time and consideration of this work.

\closing{Sincerely,}

\end{letter}
\end{document}
